IGRINS spectra of \name

### 2016-05-04 document/ms.tex
Write club outcome with Katelyn from Monay, May 2, preparing for the next formatting write club.

@@

\subsection{Full-spectrum fitting framework}
% Motivation: The questions we want to answer
Modeling the periodic light curves of spotted stars can answer these questions: ``What evidence is there to support the existence of starspots.  What constraint can be placed on the effective temperature contrast and areal coverage of the starspots?  What is the longitudinal assymetry of the spots?  ''.  As pointed out by CITE XX, cyclical light curve variations indicate only the longitudinally assymetric component of the star spots.  Photometric modeling of the light curve produces degenerate estimates in the temperature contrast and areal coverage fraction.  For example, CITE XX achieved XX.

By modeling the composite \emph{spectrum} of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.  A stellar spectrum with a longitudinaly symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating star would all show zero amplitude of photometric variability, yet they all contain star spots.  Spectroscopic modeling can still measure the starspot properties in these cases.

@@

A main motivating factor in designing our methodology was our wish to adress this question for a given spectrum: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the detection of starspots be reported?''.  In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy among themselves.  For example, we expect the best fit effective temperature contrast will be partially degenerate with the areal coverage fraction: a slightly cooler, smaller sunspot can masquerade as a larger, warmer spot.  This degeneracy should be lessened in spectroscopic methods compared to photometric methods.  The desire to reveal these intra-parameter degeneracies motivated the choice of \emph{sampling} from the posterior probability density distribution function.

@@

The main idea is that \iancze define a pixel-level forward model $\vM$ of the data.  A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.  The model encapsulates the major intrinstic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:

@@

\subsection{Approach 1: Deriving unique Teff in each order}

The model $\vM(\vT)$ was intended to apply a single set of stellar parameters to the entire wavelength range of interest, presumably the entire available spectrum.  For a spectrum from a multi-order echelle spectrograph, this means each spectral order is fit with the same stellar parameters.  Simultaneous fitting is the desired behavior for most applications involving a single stellar photospheric component.  In our case, however, we know that a single stellar photospheric component is a poor model for the data: there are \emph{two} components lurking in the composite spectrum.  But depending on the star spot properties, a single stellar photosphere component might fit the composite spectrum satisfactorily, like if the flux contrast of the starspot is simply too low compared to the noise.

@@

We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.  This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.  The na\"ive single-component fit to different wavelength provide a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.  It is conceivable that other parameters, like $\logg$ could show a dependence on wavelength if non-standard physics---\emph{i.e.}physics not included in the pre-computed model grid---mimics the effect of \emph{e.g.} $\logg$ on the spectrum.  For example, magnetic fields could cause Zeeman broadening, which could alter the derived stellar parameters $\vT_o$.  For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = \{T_{\mathrm{eff},o}, \log{g_o}, \Z_o, \Omega_{o}, v\sin{i}_o, v_{r,o}\}$ to vary by order.

@@

As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on our instrumental calibration. If the stellar parameters in one order are routinely discrepant, we can examine and refine our instrumental calibration for that spectral order.  For example, the radial velocity $v_r$ could be systematically offset in one order due to instrumental calibration problems.  Or perhaps the $v\sin{i}$ could show a dependence on wavelength, since the spectral inference framework from \iancze assumes the spectral resolution is fixed across all wavelengths, but typical spectrographs exhibit a small dependence of spectral resolution on wavelength.

@@

\subsection{Approach 2: Two component photosphere mixture model}

>>>>

Modeling the periodic light curves of spotted stars can answer these questions: ``What evidence is there to support the existence of starspots?  What constraint can be placed jointly upon the effective temperature contrast and areal coverage of the starspots?  What is the longitudinal asymmetry of the spots?  ''.  As pointed out by CITE XX, cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots.  Photometric modeling of the light curve produces degenerate estimates in the temperature contrast and areal coverage fraction.  For example, CITE XX achieved XX.

By modeling the composite \emph{spectrum} of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.  A stellar spectrum with a longitudinally symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating star would all show zero amplitude of photometric variability, yet they all contain star spots.  Spectroscopic modeling can still measure the starspot properties in these cases.

@@

\subsection{Full-spectrum fitting framework}

@@

A main motivating factor in designing our methodology was our wish to address for a given spectrum, the question: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the properties of starspots be measured?''.  In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy among themselves.  For example, we expect the best fit effective temperature contrast will be partially degenerate with the areal coverage fraction: a slightly cooler, smaller sunspot can masquerade as a larger, warmer spot.  This degeneracy should be lessened in spectroscopic methods compared to photometric methods.  The desire to reveal these intra-parameter degeneracies motivated the choice of \emph{sampling} from the posterior probability density distribution function.

@@

The main idea is that \iancze define a pixel-level forward model $\vM$ of the data.  A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.  The model encapsulates the major intrinsic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:

@@

\subsection{Model design and implementation considerations}

\subsubsection{Approach 11: Whole spectrum with a single photospheric component (Czekala et al. 2015)}

Approach 11 is identical to the strategy in \iancze.  The model $\vM(\vT)$ was intended to apply a single set of stellar parameters to the entire wavelength range of interest, presumably the entire available spectrum.  For a spectrum from a multi-order echelle spectrograph, this means each spectral order is fit with the same stellar parameters.  Simultaneous fitting is the desired behavior for most applications involving a single stellar photospheric component.  In our case, however, we know that a single stellar photospheric component is a poor model for the data: there are \emph{two or more components} lurking in the composite spectrum.  We anticipate that these fits would be too uninformative, so we did not implement Approach 11 on the whole spectrum.

\textbf{Other things to say: Optical and IR will have slightly different RV, perhaps different vsini based on erroneous spectral resolution.  This method could work with liberal assignment of local kernels, and the development of new kernels that deal with line-width mis-matches.}

\subsubsection{Approach 12: Deriving unique Teff in each order}

In local chunks of wavelength, a single stellar photosphere component might fit the composite spectrum satisfactorily.  Some wavelength chunks will fit the warm photosphere lines better and other wavelength chunks will fit prominent lines from cool spots better.  Wavelength chunks possessing lines that are present in both cool and warm stars will yield mixed results.

@@

We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.

This change does not represent reality: by definition, the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.  The na\"ive single-component fit to different wavelength chunks merely provides a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.

It is conceivable that other parameters, like $\logg$ could show a dependence on wavelength if non-standard physics---\emph{i.e.}physics not included in the pre-computed model grid---mimics the effect of \emph{e.g.} $\logg$ on the spectrum.  For example, magnetic fields could cause Zeeman broadening, which could alter the derived stellar parameters $\vT_o$.  For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = \{T_{\mathrm{eff},o}, \log{g_o}, \Z_o, \Omega_{o}, v\sin{i}_o, v_{r,o}\}$ to vary by order.

@@

As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on instrumental calibration. If the stellar parameters in one order are routinely discrepant, we can examine and refine our instrumental calibration for that spectral order.  For example, the radial velocity $v_r$ could be systematically offset in one order due to instrumental calibration problems.  Or perhaps the $v\sin{i}$ could show a dependence on wavelength, since the spectral inference framework from \iancze assumes the spectral resolution is fixed across all wavelengths, but typical spectrographs exhibit a small dependence of spectral resolution on wavelength.  (cite the SICK paper)

@@

\subsubsection{Approach 21: Whole spectrum with two components}

Ideally what we want to do is fit the entire spectrum with a two (or three, or $N_c-$component photosphere).  If we believe our model, the entire emergent spectrum of the star should be described by a single set of stellar parameters.  If nature had truly delivered a noisy version of this model, the large wavelength coverage of the

\subsubsection{Approach 22: Order-by-order with two components}

\subsection{Implementation}

\subsubsection{Mixture model definitions}
